---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: sandstone
    source: embed
params:
  df: NA
  perf: NA
  metric: NA
  yCol: NA
  dateCol: NA
  dateFormat: NA
---

---
title: `r paste0(params$metric, " ~ ", params$yCol)`
---

<style>
.navbar-fixed-top {
	background-color: #3e3f3a;
  border-color: #3e3f3a;
}

.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
    color: #ffffff;
    background-color: #393a35;
}

.navbar-default .navbar-nav>li>a {
    color: #98978b;
}

.navbar-inverse .navbar-nav>li>a {
    color: #98978b;
}

.section.sidebar {
    top: 61px;
    background-color: #f8f5f0;
}

.nav-tabs-custom > .nav-tabs > li.active {
    border-top-color: rgb(138, 138, 138);
}

</style>

```{r, echo=FALSE}
# Grab parameters and store them in variables
df <- params$df
perf <- params$perf
metric <- params$metric
yCol <- params$yCol
dateCol <- params$dateCol
dateFormat <- params$dateFormat
```


```{r, echo=FALSE}
# Correlations by date, calculations
correlSummaryDF <- data.frame(Metric = metric,
                               "Total Periods" = integer(1),
                               "Negative Periods" = integer(1),
                               "Positive Periods" = integer(1),
                               "% Negative" = numeric(1),
                               "% Positive" = numeric(1),
                               "Avg Correlation" = numeric(1),
                               check.names = FALSE)

correlSummaryDF <- data.frame(Statistic = NA,
                              Value = NA)

correlDF <- data.frame(Date = NA,
                       Correlation = NA)

# Fill in correlations by date
for(date in unique(df[, dateCol])) {

  dateDF <- df[df[,dateCol]==date, ]
  correlDF[nrow(correlDF) + 1, "Date"] <- date
  correlDF[nrow(correlDF), "Correlation"] <- cor(as.numeric(dateDF[, metric]), as.numeric(dateDF[, yCol]), use = "pairwise.complete.obs")

}

metricCorrelations <- as.numeric(correlDF$Correlation)
metricCorrelations <- metricCorrelations[!is.na(metricCorrelations)]
correlSummaryDF[1, "Statistic"] <- "Total Periods"
correlSummaryDF[1, "Value"] <- as.character(length(metricCorrelations))

correlSummaryDF[2, "Statistic"] <- "Negative Periods"
correlSummaryDF[2, "Value"] <- as.character(length(metricCorrelations[metricCorrelations < 0]))

correlSummaryDF[3, "Statistic"] <- "Positive Periods"
correlSummaryDF[3, "Value"] <- as.character(length(metricCorrelations[metricCorrelations > 0]))

correlSummaryDF[4, "Statistic"] <- "% Negative"
correlSummaryDF[4, "Value"] <- paste0(round((length(metricCorrelations[metricCorrelations < 0]) / length(metricCorrelations))*100, 2),"%")

correlSummaryDF[5, "Statistic"] <- "% Positive"
correlSummaryDF[5, "Value"] <- paste0(round((length(metricCorrelations[metricCorrelations > 0]) / length(metricCorrelations))*100, 2),"%")

correlSummaryDF[6, "Statistic"] <- "Avg Correlation"
correlSummaryDF[6, "Value"] <- as.character(round(mean(metricCorrelations, na.rm = TRUE), 2))
```

Sidebar {.sidebar}
=======================================================================

### Y Column: `r yCol`



#### Correlation Summary
```{r, results='asis'}
# Correlation by date summary
knitr::kable(correlSummaryDF)
```

#### Performance by metric quintile
```{r, results='asis'}
# Performance by metric quintile
knitr::kable(perf[, 1:2], table.attr = "id=\"perfTable\"")
```

#### Fit Summary
```{r, results='asis'}
form <- as.formula(paste0("as.numeric(", yCol, ") ~ as.numeric(", metric,")"))
fit <- lm(form, data = df)
rsq <- summary(fit)$r.squared
pval <- anova(fit)[,5][1]
dof <- anova(fit)[,1][2]

fitsummaryDF <- data.frame(Statistic = c("R-Squared", "P-Value", "Degrees of Freedom"),
                           Value = c(rsq, pval, dof))
# Correlation by date summary
knitr::kable(fitsummaryDF)
```

Plots
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Correlation by date

```{r}
# Correlation by date plot
correlDF$Date <- as.Date(correlDF$Date, format=dateFormat)
plot_ly(data = correlDF, x = ~Date, y = ~Correlation, type = 'scatter', mode = 'lines')
```

### Histogram of X Values

```{r}
# Histogram of X Values
xform <- as.formula(paste0("~",metric))
plot_ly(data = df, x = xform, type = "histogram")
```

### QQ: Metric ~ Y

```{r}
# QQ - Y
xyDF <- df[complete.cases(df[, c(metric, yCol)]), c(metric, yCol)]
sortedX <- xyDF[order(xyDF[, metric]), metric]
sortedY <- xyDF[order(xyDF[, yCol]), yCol]
xNorm <- qnorm(c(1:nrow(xyDF)) / nrow(xyDF), mean(xyDF[,metric], na.rm = TRUE), sd(xyDF[,metric], na.rm = TRUE))
xNorm <- replace(xNorm, is.infinite(xNorm), NA)
sortedDF <- data.frame(x = sortedX, y = sortedY, xNorm = xNorm)

plot_ly(data = sortedDF, x = ~x, y = ~y)
```

Data
=======================================================================
```{r, results='asis'}
knitr::kable(df)
```

<script>
for(i = 0; i < $('#perfTable th').length; i++) {
  colorTableByCol('perfTable', i);
}

function colorTableByCol(tableid, colindex){

var columnarray, maxval, minval, max, min, n;

columnarray = [];
$('#' + tableid + ' tr:not(:first)').each(function(){
	
	var val = parseFloat($(this).find('td').eq(colindex).text());
	if(val === val) {
	columnarray.push(val);
	}
	})

	maxval = Math.max(...columnarray);
	minval = Math.min(...columnarray);

	min = 0;
	if (minval > 0) {
	max = maxval;
	} else if (maxval < 0) {
	max = Math.abs(minval);
	} else {
	max = Math.max(Math.abs(maxval), Math.abs(minval));
	}

	n = max-min;

	$('#' + tableid + ' tr td:nth-child(' + (colindex + 1) + ')').each(function() {

		var val = parseFloat($(this).text());    
		var xr, xg, xb, yr, yg, yb;

		// Define the min color, which is white
		xr = 255; // Red value
		xg = 255; // Green value
		xb = 255; // Blue value

		// Define max color, depending on sign of val
		if (val >= 0) {

		// Green if val > 0, #2ca25f
		yr = 44; // Red value
		yg = 162; // Green value
		yb = 95; // Blue value

		} else {

		// Red if val < 0, #a12b2b
		yr = 161; // Red value
		yg = 43; // Green value
		yb = 43; // Blue value

		val = Math.abs(val);

		}

		// Find value's position relative to range
		var pos = ((val - min) / (n));

		// Generate RGB code
		red = parseInt((xr + (( pos * (yr - xr)))).toFixed(0));
		green = parseInt((xg + (( pos * (yg - xg)))).toFixed(0));
		blue = parseInt((xb + (( pos * (yb - xb)))).toFixed(0));

		clr = 'rgb('+red+','+green+','+blue+')';

		// Apply to cell

		$(this).css('background-color', clr);

	})
}
</script>